Analysis Stand Features 

### 2018-01-22 analysis/analysis_stand_features.Rmd
create table
stand analysis features updated 3 sites

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 May"
output:
  md_document:
    toc: true
    variant: markdown_github
---

@@

# Set levels of eleveation 
sj_lowcode  <- paste0('A', str_pad(1:10, 2, pad='0'))
sj_highcode <- paste0('A', 11:20)
ca_lowcode <- c(paste0('B', str_pad(1:10, 2, pad='0')),
            paste0('B', 26:30))
ca_highcode <- paste0('B', 11:25)

tree <- tree %>% 
  mutate(elevF = ifelse(id_focal %in% sj_lowcode, 'Low',
                       ifelse(id_focal %in% sj_highcode, 'High',
                              ifelse(id_focal %in% ca_lowcode, 'Low', 'High')))) %>%
  mutate(site = paste0(loc, '_', elevF))

# Get only focal trees  
ft <- tree %>% 
  filter(sp=='Focal') %>% 
  filter(id_focal!='Fresno') %>% 
  mutate(site = as.factor(site))

@@

```{r}
general_var <- ft %>% group_by(loc, site) %>% count()

@@

## Add code site and get centroid (see # http://rspatial.org/analysis/rst/8-pointpat.html)
sp_ca <- sp_ca %>% 
  mutate(loc = 'CA', 
         elevF = ifelse(name %in% ca_lowcode, 'Low', 'High'),
         site = paste0(loc, '_', elevF))

coord_ca <- sp_ca %>% 
  group_by(site) %>%
  summarise(lat_m = mean(lat),
            long_m = mean(long))

# plot(sp_ca$long, sp_ca$lat, pch=19, col='gray')
# points(coord_ca$long_m, coord_ca$lat_m, pch=19, col='blue')

sp_sj <- sp_sj %>% 
  mutate(loc = 'SJ', 
         elevF = ifelse(name %in% sj_lowcode, 'Low', 'High'),
         site = paste0(loc, '_', elevF))        
coord_sj <- sp_sj %>% 
  group_by(site) %>%
  summarise(lat_m = mean(lat),
            long_m = mean(long))

coords_sites <- coord_sj %>% rbind(coord_ca)

#plot(sp_sj$long, sp_sj$lat, pch=19, col='gray')
#points(coord_sj$long_m, coord_sj$lat_m, pch=19, col='blue')

coords_sites %>% kable()
```

@@

compe <- compe %>% 
  mutate(name = id_focal) %>% 
  mutate(loc = ifelse(str_detect(name, "A"), 'SJ', 'CA'),
         elevF = ifelse(name %in% sj_lowcode, 'Low',
                        ifelse(name %in% sj_highcode, 'High',
                              ifelse(name %in% ca_lowcode, 'Low', 'High')))) %>%
  mutate(site = paste0(loc, '_', elevF)) %>% 
  mutate(site = as.factor(site),
         loc = as.factor(loc),
         elevF = as.factor(elevF))

@@

  # Return also summary values 
  summ_values <- df %>% 
    dplyr::select_(mivariable, 'site') %>%
    group_by(site) %>% 
    summarise_each(funs(mean, sd, se=sd(.)/sqrt(n()), min, max))

@@

topo <- topo %>% 
  mutate(loc = ifelse(str_detect(name, "A"), 'SJ', 'CA'),
         elevF = ifelse(name %in% sj_lowcode, 'Low',
                        ifelse(name %in% sj_highcode, 'High',
                              ifelse(name %in% ca_lowcode, 'Low', 'High')))) %>%
  mutate(site = paste0(loc, '_', elevF)) %>% 
  mutate(site = as.factor(site),
         loc = as.factor(loc),
         elevF = as.factor(elevF))

# 
# topo_summary <- topo %>%
#   group_by(site) %>%
#   summarise(mde_m = mean(mde),
#             mde_sd = sd(mde),
#             mde_min = min(mde),
#             mde_max = max(mde),
#             slope_m = mean(slope),
#             slope_sd = sd(slope))
# 
# 
# 
# # Another way to obtain summary values 
# variables <- c('mde','slope','aspect')
# auxdf <- data.frame() 
# 
# for (i in variables){ 
# aux <- topo %>% 
#   dplyr::group_by(site) %>% 
#   summarise_each_(funs(mean, sd, se=sd(.)/sqrt(n())), i) %>% mutate(variable=i) 
# 
# auxdf <- rbind(auxdf, aux) }
```

@@

```{r}
## Comparison 
# Select only variables to compare 
ft_sel <- ft %>%
  mutate(dn = dn_mm / 1000, 
         h = height_cm / 100) %>% 
  dplyr::select(dn, h, site)

@@

out4 <- out3 %>% 
  transmute(variables = mivar,
            CA_High_m = round(mean_CA_High, 3),
            CA_High_sd = round(sd_CA_High, 3),
            CA_High_l = tukey_CA_High,
            CA_Low_m = round(mean_CA_Low, 3),
            CA_Low_sd = round(sd_CA_Low, 3),
            CA_Low_l = tukey_CA_Low,
            SJ_High_m = round(mean_SJ_High, 3),
            SJ_High_sd = round(sd_SJ_High, 3),
            SJ_High_l = tukey_SJ_High,
            SJ_Low_m = round(mean_SJ_Low, 3),
            SJ_Low_sd = round(sd_SJ_Low, 3),
            SJ_Low_l = tukey_SJ_Low)

# Export data 
write.csv(out4, file=paste(di, "data/proto_tables/site_features.csv", sep=""), row.names = FALSE)

## General Variables and coordinates

general_var %>% 
  left_join(coords_sites, by='site') %>% 
  write.csv(file=paste(di, "data/proto_tables/site_general.csv", sep=""), row.names = FALSE)
```

>>>>

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2018 Jan"
output:   
  md_document:
    toc: true
    variant: markdown_github
---

@@

### - old code 4 sites 
# Set levels of eleveation 
# sj_lowcode  <- paste0('A', str_pad(1:10, 2, pad='0'))
# sj_highcode <- paste0('A', 11:20)
# ca_lowcode <- c(paste0('B', str_pad(1:10, 2, pad='0')),
#             paste0('B', 26:30))
# ca_highcode <- paste0('B', 11:25)
# 
# tree <- tree %>% 
#   mutate(elevF = ifelse(id_focal %in% sj_lowcode, 'Low',
#                        ifelse(id_focal %in% sj_highcode, 'High',
#                               ifelse(id_focal %in% ca_lowcode, 'Low', 'High')))) %>%
#   mutate(site = paste0(loc, '_', elevF))
# 
#

sj_code  <- paste0('A', str_pad(1:20, 2, pad='0'))
ca_lowcode <- c(paste0('B', str_pad(1:10, 2, pad='0')), paste0('B', 26:30))
ca_highcode <- paste0('B', 11:25)

tree <- tree %>% mutate(
  site = as.factor(case_when(
    id_focal %in% sj_code ~ "sj", 
    id_focal %in% ca_highcode ~ "caH", 
    id_focal %in% ca_lowcode ~ "caL")))

# Get only focal trees  
ft <- tree %>% 
  filter(sp=='Focal') %>% 
  filter(id_focal!='Fresno')

@@

```{r}
general_var <- ft %>% group_by(site) %>% count()

@@

sp_sites <- rbind(sp_sj, sp_ca) %>% 
  mutate(site = as.factor(case_when(
    name %in% sj_code ~ "sj", 
    name %in% ca_highcode ~ "caH", 
    name %in% ca_lowcode ~ "caL")))

coord_sites <- sp_sites %>% 
  group_by(site) %>%
  dplyr::summarise(lat_m = mean(lat), long_m = mean(long))

coord_sites %>% kable()

# old code 
# 
# 
# 
# ## Add code site and get centroid (see # http://rspatial.org/analysis/rst/8-pointpat.html)
# sp_ca <- sp_ca %>% 
#   mutate(loc = 'CA', 
#          
#          
#          elevF = ifelse(name %in% ca_lowcode, 'Low', 'High'),
#          site = paste0(loc, '_', elevF)) 
# 
# coord_ca <- sp_ca %>% 
#   group_by(site) %>%
#   summarise(lat_m = mean(lat),
#             long_m = mean(long))
# 
# # plot(sp_ca$long, sp_ca$lat, pch=19, col='gray')
# # points(coord_ca$long_m, coord_ca$lat_m, pch=19, col='blue')
#   
# sp_sj <- sp_sj %>% 
#   mutate(loc = 'SJ', 
#          elevF = ifelse(name %in% sj_lowcode, 'Low', 'High'),
#          site = paste0(loc, '_', elevF))        
# coord_sj <- sp_sj %>% 
#   group_by(site) %>%
#   summarise(lat_m = mean(lat),
#             long_m = mean(long))
# 
# coords_sites <- coord_sj %>% rbind(coord_ca)
# 
# #plot(sp_sj$long, sp_sj$lat, pch=19, col='gray')
# #points(coord_sj$long_m, coord_sj$lat_m, pch=19, col='blue')
# 
# coords_sites %>% kable()
```

@@

compe <- compe %>% 
  mutate(site = as.factor(case_when(
    id_focal %in% sj_code ~ "sj", 
    id_focal %in% ca_highcode ~ "caH", 
    id_focal %in% ca_lowcode ~ "caL")))

# old code 
# compe <- compe %>% 
#   mutate(name = id_focal) %>% 
#   mutate(loc = ifelse(str_detect(name, "A"), 'SJ', 'CA'),
#          elevF = ifelse(name %in% sj_lowcode, 'Low',
#                         ifelse(name %in% sj_highcode, 'High',
#                               ifelse(name %in% ca_lowcode, 'Low', 'High')))) %>%
#   mutate(site = paste0(loc, '_', elevF)) %>% 
#   mutate(site = as.factor(site),
#          loc = as.factor(loc),
#          elevF = as.factor(elevF))

@@

  # Return also summary values 
  summ_values <- df %>% 
    dplyr::select_(mivariable, 'site') %>%
    group_by(site) %>% 
    summarise_all(funs(mean, sd, se=sd(.)/sqrt(n()), min, max))

@@

# topo <- topo %>% 
#   mutate(loc = ifelse(str_detect(name, "A"), 'SJ', 'CA'),
#          elevF = ifelse(name %in% sj_lowcode, 'Low',
#                         ifelse(name %in% sj_highcode, 'High',
#                               ifelse(name %in% ca_lowcode, 'Low', 'High')))) %>%
#   mutate(site = paste0(loc, '_', elevF)) %>% 
#   mutate(site = as.factor(site),
#          loc = as.factor(loc),
#          elevF = as.factor(elevF))

topo <- topo %>% 
  mutate(site = as.factor(case_when(
    name %in% sj_code ~ "sj", 
    name %in% ca_highcode ~ "caH", 
    name %in% ca_lowcode ~ "caL")))

@@

```{r}
## Comparison 
# Select only variables to compare 
ft_sel <- ft %>%
  mutate(dn = dn_mm / 10, 
         h = height_cm / 100) %>% 
  dplyr::select(dn, h, site)

@@

# out4 <- out3 %>% 
#   transmute(variables = mivar,
#             CA_High_m = round(mean_CA_High, 3),
#             CA_High_sd = round(sd_CA_High, 3),
#             CA_High_l = tukey_CA_High,
#             CA_Low_m = round(mean_CA_Low, 3),
#             CA_Low_sd = round(sd_CA_Low, 3),
#             CA_Low_l = tukey_CA_Low,
#             SJ_High_m = round(mean_SJ_High, 3),
#             SJ_High_sd = round(sd_SJ_High, 3),
#             SJ_High_l = tukey_SJ_High,
#             SJ_Low_m = round(mean_SJ_Low, 3),
#             SJ_Low_sd = round(sd_SJ_Low, 3),
#             SJ_Low_l = tukey_SJ_Low)

out4 <- out3 %>% 
  transmute(variables = mivar,
            caH_m = round(mean_caH, 3),
            caH_sd = round(sd_caH, 3),
            caH_l = tukey_caH,
            caL_m = round(mean_caL, 3),
            caL_sd = round(sd_caL, 3),
            caL_l = tukey_caL,
            sj_m = round(mean_sj, 3),
            sj_sd = round(sd_sj, 3),
            sj_l = tukey_sj)

# Export data 
# write.csv(out4, file=paste(di, "data/proto_tables/site_features.csv", sep=""), row.names = FALSE)
write.csv(out4, file=paste(di, "data/competence/resumen_medias_indices_competencia.csv", sep=""), row.names = FALSE)

pander(out4, caption='Summary Values')
```

# General topo of the sites

```{r}
topo_site <- topo %>% group_by(site) %>% summarise(
  elev_mean = mean(mde), 
  elev_min = min(mde), 
  elev_max = max(mde), 
  slope_mean = mean(slope)
)

site_general <- general_var %>% 
  left_join(coord_sites, by='site') %>% 
  left_join(topo_site, by='site')

write.csv(site_general, file=paste(di, "data/sites_summary/site_general.csv", sep=""), row.names = FALSE)
```
